Delta Smelt Enclosure Study 2019 Hybrid Paper Diet Analysis

### 2022-11-21 smelt_2019_allseasons/Diet 2019.Rmd
zoop and diet plot updates

#sum for taxa abundance among individual fish
taxa_tag<- diet %>% 
  group_by(Location, Mesh, tlc, Taxa) %>% 
  summarize("count.sum"= sum(Count))

#sum taxa across stomach
stomach<- diet %>% 
  group_by(Location, Mesh, tlc) %>% 
  summarize("stomach.sum"= sum(Count))

@@

#replace count.sum Nas with zeros
full.count<-full.prop.2 %>% replace_na(list(count.sum=0))

#select columns I want for count
full.count<-subset(full.count, select=c("Location", "Mesh", "tlc", "Taxa", "count.sum"))

#select columns I want for proportion
full.prop.3<-subset(full.prop.2, select=c("Location", "Mesh", "tlc", "Taxa", "proportion"))

@@

library(scales)
show_col(viridis_pal(option = "plasma")(8))
viridis_pal(option = "plasma")(8)

ggsave("smelt_2019_allseasons/figures/diet19_multipanel.png", dpi=250, height=6, width=6, units="in")
```

### Plot methods text (from manuscript): To visualize the relative abundance of different taxa among mesh types, we calculated taxa proportion (taxa abundance/total abundance) for each individual fish’s diet and then averaged these taxa proportions across individuals from each mesh type. These means were then fit to a 100% scale to estimate the mean percent contribution of each taxa to overall mesh type diets. Averaging proportions instead of abundance across fish allowed for the diets of different sizes fish to contribute equally.

>>>>

#sum for taxa abundance among individual fish
taxa_tag<- diet %>% 
  group_by(Location, tlc, Taxa) %>% 
  summarize("count.sum"= sum(Count))

#sum taxa across stomach
stomach<- diet %>% 
  group_by(Location, tlc) %>% 
  summarize("stomach.sum"= sum(Count))

@@

#select columns I want for proportion
full.prop.3<-subset(full.prop.2, select=c("Location", "tlc", "Taxa", "proportion"))

@@

ggsave("smelt_2019_allseasons/figures/diet19_multipanel.png", dpi=250, height=6, width=6, units="in")

library(scales)
show_col(viridis_pal(option = "plasma")(8))
viridis_pal(option = "plasma")(8)
```

### 2022-11-21 smelt_2019_allseasons/Zoop 2019.Rmd
zoop and diet plot updates

ggplot() +
  geom_bar(position = "fill", stat = "identity", data=caught.sea2, aes (x=Location, y=sum.count, fill=Taxa), colour="black", width = .75) +
  facet_wrap(~Season, ncol = 1) +
  theme_bw() + 
  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
  labs(x = "Location") +
  labs(y = "Relative Abundance")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10))

>>>>

#create custom palette from viridis to match taxa from diet plot
zoopPalette <- c("#0D0887FF", "#5402A3FF", "#8B0AA5FF", "#B93289FF", "#DB5C68FF", "#F48849FF")

ggplot() +
  geom_bar(position = "fill", stat = "identity", data=caught.sea2, aes (x=Location, y=sum.count, fill=Taxa), colour="black", width = .75) +
  facet_wrap(~Season, ncol = 1) +
  theme_bw() + 
  scale_fill_manual(values=zoopPalette)+
  labs(x = "Location") +
  labs(y = "Relative Abundance")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10))
